Towards Verifying the Bitcoin-S Library

### 2019-06-21 paper/paper.tex
changed from BigInt with Long comparison to BigInt with BigInt comparison
before and after for concrete type

@@

This error is hard to understand, but we can see that there is a missing Long to BigInt conversion.
So we search for all Long values in the code.
\begin{lstlisting}[style=scala]
  private case class Int64Impl(underlying: BigInt) extends Int64 {
    require(underlying >= -9223372036854775808L)
    require(underlying <= 9223372036854775807L)
  }
\end{lstlisting}

>>>>

Before:
\begin{lstlisting}[style=scala]
sealed abstract class Number {
  type A = BigInt

  /**
    * Checks if the given result is within the range
    * of this number type
    */
  private def checkResult(result: BigInt): A = {
    require(
          result <= BigInt("9223372036854775807")
      && result >= BigInt("-9223372036854775808"))
    result
  }
}

After:
\begin{lstlisting}[style=scala]
sealed abstract class Number {
  /** The underlying scala number used to to hold the number */
  protected def underlying: BigInt

  /** Factory function to create the underlying T, for instance a UInt32 */
  def apply: BigInt => Int64

  /**
    * Checks if the given result is within the range
    * of this number type
    */
  private def checkResult(result: BigInt): BigInt = {
    require(
         result <= BigInt("9223372036854775807")
      && result >= BigInt("-9223372036854775808"))
    result
  }
}

/**
  * Represents a int64_t in C
  */
sealed abstract class Int64 extends SignedNumber {
  override def apply: BigInt => Int64 = Int64(_)
}
\end{lstlisting}

@@

This error is hard to understand, but we can see that there is a missing Long to BigInt conversion.
So we search for all Long values in the code.

Before:
\begin{lstlisting}[style=scala]
private case class Int64Impl(underlying: BigInt) extends Int64 {
  require(underlying >= -9223372036854775808L)
  require(underlying <= 9223372036854775807L)
}
\end{lstlisting}

After:
\begin{lstlisting}[style=scala]
private case class Int64Impl(underlying: BigInt) extends Int64 {
  require(underlying >= BigInt("-9223372036854775808"))
  require(underlying <= BigInt("9223372036854775807"))
}  
\end{lstlisting}
